Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-03 paper/ijm.tex
Update ijm.tex
Small changes in Chapter 4 model (1) and more detail description of model 2

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: 
		\\alpha_{g}{}' X_{it}^{g}+
		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_t^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

We estimate three models that differ in terms of the number of
control variables. The first one only includes the language skills
and year dummies. The second one also includes individual
characteristics, such as age, education, and county of residence.
Finally, the third model also includes industry, occupation, and other
workplace descriptors.

>>>>

%\fxnote{Add here another index g to denote the group? I used it in other articles, because it was requested and it makes sense}
We estimate the basic model in the following form:
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: 
		\\alpha^{g}{}' X_{it}^{g}+
		\\& + \vec{beta}^{g}{}' \cdot \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t}^{g} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y_{it}^{g}$ is the outcome (either unemployment indicator
or logarithm of net monthly wage)
of individual $i$ in wave $t$ from ethnic group g; $\vec{X}^{g}$ are the other individual
characteristics for both groups; $L$ is the vector of
language skill descriptors, $eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}^{g}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. We denote the groups g by E (Estonian) and R (Russian).
As we use panel data, we cluster the
standard errors on individuals.  When analysing the time trend, we
replace the main language effects in~\eqref{eq:specification} by the
\fxnote*{Did we estimate it really that way? At least not in my code.}{corresponding interactions}
\begin{align}
	\label{eq:time_interaction}
	\beta_{RUS,t} \cdot RUS_{it} \cdot \upsilon_{t} +
	\beta_{EST,t} \cdot EST_{it} \cdot \upsilon_{t} +
	\beta_{ENG,t} \cdot ENG_{it} \cdot \upsilon_{t}.
\end{align}

We estimate three models that differ in terms of the number of
control variables. The first one only includes the language skills
and year dummies. The second one also includes individual
characteristics (age, education) and family descriptors (marital status, having kids up to 17 years old) and county of residence.
Finally, the third model additionally includes industry, occupation, and other
workplace descriptors.
